The \project{unRAVE} catalog

### 2016-09-03 article/unrave.tex
Edited text and rearranged up to sect 3.3

The target selection for \rave\ is based on the $I$-band apparent magnitude,
$9 < I < 12$, with a weak $J - K_s > 0.5$ cut near the disk and bulge \citep{Wonjo_2016}.  
The $I$ band was used for the target selection because it has a good overlap with the
wavelength range that \rave\ operates in:  8410--8795~\AA.  This spectral region 
is very well-studied.  It is one of the key setups used for the ground-based 
high-resolution \ges\ survey \citep{Gilmore_2012,Randich_2013}, and the 
\rave\ resolution and wavelength coverage is comparable to the Radial Velocity 
Spectrometer on board the \gaia\ space telescope \citep{Kordopatis_2011,Recio-Blanco_2016}.  
The region includes the \ion{Ca}{2} near infrared triplet lines --- strong 
transitions that are dominated by pressure broadening --- which are visible even 
in very low S/N data or metal-poor stars.  Atomic transitions of light-, $\alpha$-, 
and Fe-peak elements are also present, allowing for detailed chemical abundance studies.

The exposure times for \rave\ observations were optimised to obtain radial 
velocities for as many stars as possible.  Detailed chemical abundances were
always an important science goal of the survey, but this was a secondary objective.  
For this reason the distribution of S/N ratios in \rave\ spectra is considerably 
lower than other stellar spectroscopic surveys where chemical abundances are the 
primary motivation.  The \rave\ spectra have an effective resolution 
$\mathcal{R} \approx 7500$ and the distribution of S/N ratios peaks at 
$\approx$50~per~pixel$^{-1}$.  For comparison, the \galah\ survey 
\citep{DeSilva_2015} --- which was specifically constructed for detailed chemical 
abundance analyses --- includes a wavelength range about 2.5 times larger at 
resolution $\mathcal{R} \approx 28,000$, and yet the \galah\ project still 
targets for S/N $\gtrsim100$.

Despite the relatively low resolution and S/N of the spectra compared to other
surveys, the \rave\ data releases have demonstrated the team's enormous success 
in deriving radial velocities, stellar astrophysical parameters ($\teff$, $\logg$),
as well as individual chemical abundances \citep{Steinmetz_2006,Zwitter_2008,
Siebert_2011,Kordopatis_2013,Kunder_2016}.  In this work we make use of spectra
that has been reprocessed for the fifth \rave\ data release.  These re-processing
steps include: a detailed re-reduction of all the original data frames, with flux
variances propagated at every step; an updated continuum-normalization procedure;
as well as revised determinations of stellar radial velocities and morphological
classifications. At the end of this processing for each survey observation we are 
provided with: rest-frame wavelengths, continuum-normalized fluxes, fractional 
uncertainties in continuum-normalized flux values, as well as relevant metadata.  
We refer the reader to the official fifth data release paper of the \rave\ survey, 
as presented by \citet{Kunder_2016}, for more details of this re-processing.

Given the high-quality of the normalization performed by the \rave\ team, we chose
not to re-normalize the spectra.  Our tests demonstrated that the procedure 
outlined in \citet{Kunder_2016} is sufficient for our analysis procedure. Therefore,
there is a limited number of pre-processing steps that we conducted before our
analysis could begin.  First, we calculated inverse variance arrays from the
fractional uncertainties provided, and then re-sampled the flux and inverse variance
arrays onto a common rest-wavelength map for all stars.  Depending on the fibre 
used and the stellar radial velocity, the range of rest-frame wavelength values
varied for each star.  Given that fluxes were unavailable in the edge pixels for 
most stars, we excluded pixels outside of the rest wavelength range 
$8423.2\,{\rm \AA} \le \lambda \le 8777.6\,{\rm \AA}$.  This corresponds to about
30~pixels excluded on either side of the common wavelength array, leaving us with
945~pixels per spectrum for science.

@@

We chose to adopt a data-driven model --- rather than a physics-driven model ---
for this analysis.  Specifically we will use an implementation of \thecannon\
\citep{Ness_2015,Ness_2016}.  Although this choice complicated the construction 
of our model (e.g., see Section \ref{sec:the-training-set}), a data-driven model 
makes use of all available information in the spectrum and lowers the S/N ratio 
at which systematic effects begin to dominate.  In other words, a well-constructed
data-driven model will yield more precise labels (e.g., stellar parameters and
chemical abundances) at low S/N ratios than most physics-driven models\footnote{
However, see \citet{Casey_2016a}}.  This is particularly relevant for the 
low-resolution \rave\ data analysed here, because about half of the spectra have
S/N $\lesssim 50$.

\noindent{}Our work makes the following assumptions about the \rave\ spectra and \thecannon:

\begin{itemize}
\item We will assume that any fibre- and time-dependent variations in spectral
resolution in the \rave\ spectra are negligible.
\item The \rave\ noise variances are approximately correct, independent between
pixels, and normally distributed.
\item We assume that the normalization procedure employed by the \rave\ pipeline
is invariant with respect to the labels, and invariant with respect to the S/N
ratio.
\item We assume that stars with similar labels ($\teff$, $\logg$, and abundances)
have similar spectra.
\item A stellar spectrum is a smooth function of the label values for that star,
and we assume that the function is smooth enough within a sub-space of the labels
(e.g., the giant branch or the main-sequence) that it can be reasonably approximated 
with a low-order polynomial in label space.
\item We have constructed a training set of stars with mean accurate labels.  Note
that we do not assume that \emph{every} label in the training is accurate -- we can
afford to have a small fraction of inaccurate labels (e.g., unambiguous misclassifications
present in the training set).
\item We assume our training set is representative of the test set (the \rave\ survey).
\end{itemize}

We adopt the nomenclature first set out in \citet{Ness_2015}, and extended in 
\citet{Casey_2016b}.  However, one distinction here with \citet{Casey_2016b} is 
that in this work the \emph{labelled} set and the \emph{training} set will be 
the same set.  In \citet{Casey_2016b} two subsets of the labelled set were 
defined: the training set and a distinct validation set.  This allowing us to 
train on the \emph{training set} and then test on the \emph{validation set}.  
However in this work the labelled set is relatively small, about an order of 
magnitude smaller than what was available in \citet{Casey_2016b}, and therefore 
no validation set exists. We will use all labelled set stars in the training 
step and supplement our validation experiments with literature comparisons.  
Thus, throughout this work we will use the terms \emph{labelled set} and 
\emph{training set} interchangeably.

We sought to construct a training set consisting of stars across the main-sequence,
sub-giant, and the red giant branch.  We required stars with precisely measured
effective temperature $\teff$, surface gravity $\logg$, and elemental abundances
of Fe, Mg, Si, Ti, Ca, Al, and Ni.  This proved to be difficult because the magnitude
range of \rave\ does not overlap substantially with high-resolution spectroscopic
surveys.  The fourth internal data release of the \ges\ survey includes 
giant and main-sequence stars, but only 142 overlap with \rave.  The thirteenth data 
release from \sdss\ \citep{sloan_dr13} includes labels for \apogee\ stars on the
giant branch and (uncalibrated values for) the main-sequence, but our tests indicated
that the \apogee\ main-sequence labels suffered from significant systematic effects.  A flat, 
then `up-turning' main-sequence is present, and the metallicity gradient trends in 
the opposite direction with respect to $\logg$ on the main-sequence (i.e., metal-poor
stars incorrectly sit above the isochrones in a classical Hertzsprung-Russell diagram).
If we consider lower-resolution studies as potential training sets, there are 2,369
stars that overlap with \lamost\ --- of which 2,213 have positive S/N ratios in the 
$g$-band (\texttt{snrg}).  However, the labels are expectedly less precise given the
lower resolution, no detailed abundance information is available for main-sequence 
stars\footnote{Abundance information is available for \lamost\ stars from \citet{Ho_2016},
but that sample contains only giant stars}, and similar systematic trends are apparent
in the lower main-sequence.  The \galah\ survey has a good overlap with \rave, but 
results from that sample are not yet precise enough for our purposes.

These constraints forced us to construct a heterogeneous training set.  Given previous
successes in transferring high S/N ratio labels from \apogee\ \citep{Ness_2015,
Ness_2016,Ho_2016,Casey_2016b}, we chose to use the 1,355 stars in the \apogee---\rave\ 
overlap sample for giant star labels in the training set.  Of these, about 900 are 
giants according to \apogee.  From this sample we selected stars to have: metallicity
determinations ([Fe/H] $> -5$); high S/N ratios in both the \apogee\ and \rave\ spectra
($>200$ in \apogee; $>50$ in \rave); and we further required that the \aspcap\ pipeline 
did not report any peculiar flags (\texttt{ASPCAPFLAG = 0}).  These restrictions left 
us with 357 stars along the giant branch, with metallicities ranging from 
$[{\rm Fe/H}] = -1.62$ to 0.32.  Intermediate tests with globular cluster members showed
that the metallicity range of the training set needed to extend below 
$[{\rm Fe/H}] \lesssim -2$ in order for our catalog to be practically useful.
Therefore, as we will describe in more detail below, we supplemented this sample with 
giant stars from the \epic\ catalog \citep{Huber_2016}.

Assembling a training set for the main-sequence and sub-giant branch was more complex.
There are no spectroscopic studies that have a large enough sample size that overlap 
with \rave, and which also cover our required range in stellar parameters 
(e.g., FGKM-type stars).  Moreover, most of the spectroscopic studies we considered 
exhibit a flat lower main-sequence, a systematic consequence of the analysis method 
adopted \citep[e.g., see][for a discussion]{Bensby_2014}.  For these reasons we chose
to make use of the \epic\ catalog \citep{Huber_2016} for the training set labels on
the main-sequence and sub-giant branch.  The \epic\ catalog follows from the successful
\project{Kepler} input catalog \citep{Brown_2011}, and provides probabilistic stellar 
classifications for 138,600 stars in the \project{K2} fields based on the 
astrometric, asteroseismic, photometric, and spectroscopic information available for
every star.  There are 4,611 stars that overlap between \epic\ and \rave.

\epic\ differs from the \project{Kepler} input catalog because \epic\ does not 
benefit from having narrow-band $DDO_{51}$ photometry in order to aid dwarf/giant 
classification.  Despite this limitation the labels in the \epic\ catalog have 
already been shown to be accurate and trustworthy \citep{Huber_2016}.  However, 
when the posteriors are wide (i.e., the quoted confidence intervals are large) 
due to limited information available, it is possible that a star has been 
mis-classified.  This is most prevalent for sub-giants, where \citet{Huber_2016} 
note that $\approx55-70$\% of sub-giants are misclassified as dwarfs.  The 
probability of misclassification is usually quantified in the uncertainties of 
each star; most sub-giants that could be dwarfs have large confidence intervals.  
Therefore, requiring low uncertainties will decrease the total sample size, but 
in practice it removes most misclassifications.  The situation is far more favourable for 
dwarfs and giants.  Only $1-4$\% of giant stars are misclassified as dwarfs, and 
about 7\% of dwarfs are misclassified as giants.  To summarise, the \epic\ labels 
with narrow confidence intervals are usually of high fidelity, and any spurious 
misclassifications would be clearly distinguishable if spectra were available.

We sought to have a small overlap between our giant and main-sequence star training
sets.  Most of our giant training set is encapsulated within $0 < \logg < 3.5$, 
however there is a sparse sampling of stars reaching to $\logg \approx 4$.  For
the \epic\ main-sequence/sub-giant star training set we required $\logg > 3.5$,
allowing for $\approx0.5$~dex of overlap between the two training sets.  We further
employed the following quality constraints: the upper and lower confidence intervals 
in $\teff$ must be below 150~K; the upper and lower confidence intervals in $\logg$ 
must be less than 0.15~dex; the $S/N$ of the \rave\ spectra must exceed 
30~per~pixel$^{-1}$; and $\teff \leqslant 6750$~K.  Unfortunately these strict constraints
removed most metal-poor stars, which we later found to cause the test labels to have
under-predicted abundances for dwarfs of low metallicity.  For this reason we relaxed
(ignored) those quality constraints for stars in the \epic\ catalog with 
$[{\rm Fe/H}] < -1$.  Of the stars we forcibly included with $[{\rm Fe/H}] < -1$,
none were classified as being sub-giants in \epic, therefore they have a low (7\%)
likelihood of misclassification.  After training a model based on main-sequence and
giant stars (Section \ref{sec:the-model}), we found we could further identify 
misclassifications by leave-one-out cross-validation (iteratively, even).  However,
we chose not to do this because the number of likely misclassifications in the training
set was negligible ($\approx1$\%), and the improvement in main-sequence test set labels
was minimal.  The distilled sample of the \rave--\epic\ overlap catalog contains 583 
stars (of 4,611).

We have constructed a justified training set for stars across the main-sequence, sub-giant,
and red giant branch.  However the lack of overlap between \rave\ and other works have
resulted in a somewhat peculiar situation. Detailed abundances are available from \apogee\
for all giant stars in our sample, but only imprecise metallicities are available from
\epic\ for stars on the main-sequence and the sub-giant branch.  To our knowledge this 
problem has not been addressed with data-driven models in the astrophysics literature.
In the following section we will construct a simplified model that does not include detailed
abundances, before demonstrating how we (1) improve upon the imprecise metallicities for 
main-sequence/sub-giant stars, and (2) translate abundances from the giant branch stars 
to the main-sequence/sub-giant branch sample.

@@

\noindent{}The model we adopt is
\begin{eqnarray}\label{eq:model}
y_{jn} & = & \vecv(\ell_n)\cdot\vectheta_j + e_{jn}\quad ,
\end{eqnarray}

\noindent{}where $y_{jn}$ is the pseudo-continuum-normalized flux for star $n$ at wavelength pixel
$j$, $\vecv(\ell_n)$ is the vectorizing function that takes as input the $K$ labels
$\ell_n$ for star $n$ and outputs functions of those labels as a vector of length
$D>K$, $\vectheta_j$ is a vector of length $D$ of parameters influencing the model at
wavelength pixel $j$, and $e_{jn}$ is the residual (noise).  Here we will only consider
vectorizing functions with polynomial expansions (e.g., $\teff^2$, see Section 
\ref{sec:a-simple-model}).  The noise values $e_{jn}$ can be considered to be drawn 
from a Gaussian distribution with zero mean and variance $\sigma_{jn}^2 + s_j^2$, where
$\sigma_{jn}^2$ is the variance in flux $y_{jn}$ and $s_j^2$ describes the excess 
variance at the $j$-th wavelength pixel.  We direct the reader to \citet{Ness_2015} for
a more detailed introduction and justification of \thecannon.

At the training step we fix the $K$-lists of labels for all the training set stars $n$.
At each wavelength pixel $j$, we then calculate the parameters $\vectheta_j$ and $s_j^2$
by optimizing the penalized likelihood function:
\begin{eqnarray}\label{eq:train}
\vectheta_j,s^2_j &\leftarrow& \argmin{\vectheta,s}\left[
    \sum_{n=0}^{N-1} \frac{[y_{jn}-\vecv(\ell_n)\cdot\vectheta]^2}{\sigma^2_{jn}+s^2}
    + \sum_{n=0}^{N-1} \ln(\sigma^2_{jn}+s^2) + \Lambda{}Q(\vectheta)
    \right]
  \quad ,
\end{eqnarray}

@@

Note that the $d$ subscript here is zero-indexed; the function $Q(\vectheta)$ does not act
on the (first) $\theta_0$ coefficient, as this is a `pivot point' or offset that we do not
expect to diminish with increasing regularization (e.g., see equation 
\ref{eq:vectorizer-three-label-design-matrix}).  In practice equation \ref{eq:train} is 
optimized by fixing $s_j^2 = 0$ to make equation~\ref{eq:train} a convex optimization 
problem, then we optimize for $\vectheta_j$, before solving for $s_j^2$.

@@

@@

The model we have introduced is generic in the sense that there is no description for how
complex the vectorizing function $\vecv(\ell)$ should be, or how many $K$ labels are used.
Given previous successes using a second-order (quadratic) polynomial model 
\citep{Ness_2015,Ness_2016,Ho_2016,Casey_2016b}, we will first adopt a three-label ($\teff$, $\logg$, [Fe/H]) model for all (giant and main-sequence) stars. Thus, for our first set of
model experiments,
\begin{eqnarray}\label{eq:vectorizer-three-label}
\vecv(\ell_n) \rightarrow \left[1, T_{{\rm eff},n}, \logg_n, [{\rm Fe/H}]_n, T_{{\rm eff},n}^2, \logg_n\cdot{}T_{{\rm eff},n}, \feh_n\cdot{}T_{{\rm eff},n}, \logg_n^2, \feh_n\cdot\logg_n, \feh_n^2\right]
\end{eqnarray}

>>>>

The target selection for \rave\ is based on the $I$-band apparent magnitude,
$9 < I < 12$, with a weak $J - K_s > 0.5$ cut near the disk and bulge \citep{Wonjo_2016}.  
The $I$ band was used for the target selection because it has a good overlap with the
wavelength range that \rave\ operates in:  8410--8795~\AA.  This spectral region 
is very well-studied.  It is one of the key setups used for the ground-based 
high-resolution \ges\ survey \citep{Gilmore_2012,Randich_2013}, and the 
\rave\ resolution and wavelength coverage is comparable to the Radial Velocity 
Spectrometer on board the \gaia\ space telescope \citep{Kordopatis_2011,Recio-Blanco_2016}.  
The region includes the \ion{Ca}{2} near infrared triplet lines --- strong 
transitions that are dominated by pressure broadening --- which are visible even 
in very low signal-to-noise (S/N) data or metal-poor stars.  Atomic transitions of 
light-, $\alpha$-, and Fe-peak elements are also present, allowing for detailed 
chemical abundance studies.

The exposure times for \rave\ observations were optimised to obtain radial 
velocities for as many stars as possible.  Detailed chemical abundances were
always an important science goal of the survey, but this was a secondary objective.  
For this reason the distribution of S/N ratios in \rave\ spectra is considerably 
lower than other stellar spectroscopic surveys where chemical abundances are the 
primary motivation.  The \rave\ spectra have an effective resolution 
$\mathcal{R} \approx 7{,}500$ and the distribution of S/N ratios peaks at 
$\approx$50~pixel$^{-1}$.  For comparison, the \galah\ survey 
\citep{DeSilva_2015} --- which was specifically constructed for detailed chemical 
abundance analyses --- includes a wavelength range about 2.5 times larger at 
resolution $\mathcal{R} \approx 28{,}000$, and yet the \galah\ project still 
targets for S/N $\gtrsim100$.

Despite the relatively low resolution and S/N of the spectra compared to other
surveys, the \rave\ data releases have demonstrated the team's enormous success 
in deriving radial velocities, stellar astrophysical parameters ($\teff$, $\logg$),
as well as individual chemical abundances \citep{Steinmetz_2006,Zwitter_2008,
Siebert_2011,Kordopatis_2013,Kunder_2016}.  In this work we make use of spectra
that has been reprocessed for the fifth \rave\ data release.  These re-processing
steps include: a detailed re-reduction of all the original data frames, with flux
variances propagated at every step; an updated continuum-normalization procedure;
as well as revised determinations of stellar radial velocities and morphological
classifications. At the end of this processing for each survey observation we were 
provided with: rest-frame wavelengths (without resampling), continuum-normalized 
fluxes, $1\sigma$ uncertainties in the continuum-normalized flux values, as well 
as relevant metadata for each observation.  We refer the reader to the official 
fifth data release paper of the \rave\ survey, as presented by \citet{Kunder_2016}, 
for more details of this re-processing.

Given the high-quality of the normalization performed by the \rave\ team, we chose
not to re-normalize the spectra.  Our tests demonstrated that the procedure 
outlined in \citet{Kunder_2016} is sufficient for our analysis procedure. Therefore,
there is a limited number of pre-processing steps that we conducted before our
analysis began.  First, we calculated inverse variance arrays from the $1\sigma$ 
uncertainties provided, and then we re-sampled the flux and inverse variance
arrays onto a common rest-wavelength map for all stars.  Depending on the fibre 
used and the stellar radial velocity, the range of rest-frame wavelength values
varied for each star.  Given that fluxes were unavailable in the edge pixels for 
most stars, we excluded pixels outside of the rest wavelength range 
$8423.2\,{\rm \AA} \le \lambda \le 8777.6\,{\rm \AA}$.  This corresponds to about
30~pixels excluded on either side of the common wavelength array, leaving us with
945~pixels per spectrum for science.

@@

We chose to adopt a data-driven model --- rather than a physics-based model ---
for this analysis.  Specifically, we will use an implementation of \thecannon\
\citep{Ness_2015,Ness_2016}.  Although this choice complicated the construction 
of our model (e.g., see Section \ref{sec:the-training-set}), a data-driven approach 
makes use of all available information in the spectrum and lowers the S/N ratio 
at which systematic effects begin to dominate.  In other words, in the low S/N
regime, a well-constructed data-driven model will yield more precise labels 
(e.g., stellar parameters and chemical abundances) than most physics-driven 
models\footnote{However, see \citet{Casey_2016a}}.  This is particularly relevant 
for the low-resolution \rave\ data analysed here, because about half of the 
spectra have S/N $\lesssim 50$.

There are two main analysis steps when using \thecannon: the \emph{training} 
step and the \emph{test} step.  These stages are briefly described in the
following section, and a more thorough introduction can be found in \citet{Ness_2015}.
We make the following explicit assumptions about the \rave\ spectra and \thecannon:

\begin{itemize}
\item We assume that any fibre- and time-dependent variations in spectral
resolution in the \rave\ spectra are negligible.
\item The \rave\ noise variances are approximately correct, independent between
pixels, and normally distributed.
\item We assume that the normalization procedure employed by the \rave\ pipeline
is invariant with respect to the labels we seek to measure, and invariant with 
respect to the S/N ratio.
\item We assume that stars with similar labels ($\teff$, $\logg$, and abundances)
have similar spectra.
\item A stellar spectrum is a smooth function of the label values for that star,
and we assume that the function is smooth enough within a sub-space of the labels
(e.g., the giant branch or the main-sequence) that it can be reasonably approximated 
with a low-order polynomial in label space.
\item We have constructed a training set of stars with mean accurate labels.  Note
that we do not assume that \emph{every} label in the training is accurate -- we can
afford to have a small fraction of inaccurate labels (e.g., a few obvious 
misclassifications in the training set are affordable).
\item We assume our training set is representative of the test set (the \rave\ survey).
\end{itemize}

%We adopt the nomenclature first set out in \citet{Ness_2015}, and extended in 
%\citet{Casey_2016b}.  However, one distinction here with \citet{Casey_2016b} is 
%that in this work the \emph{labelled} set and the \emph{training} set will be 
%the same set.  In \citet{Casey_2016b} two subsets of the labelled set were 
%defined: the training set and a distinct validation set.  This allowing us to 
%train on the \emph{training set} and then test on the \emph{validation set}.  
%However in this work the labelled set is relatively small, about an order of 
%magnitude smaller than what was available in \citet{Casey_2016b}, and therefore 
%no validation set exists. We will use all labelled set stars in the training 
%step and supplement our validation experiments with literature comparisons.  
%Thus, throughout this work we will use the terms \emph{labelled set} and 
%\emph{training set} interchangeably.

@@

\noindent{}Given our assumptions, the model we adopt is
\begin{eqnarray}\label{eq:model}
y_{jn} & = & \vecv(\ell_n)\cdot\vectheta_j + e_{jn}\quad ,
\end{eqnarray}

\noindent{}where $y_{jn}$ is the pseudo-continuum-normalized flux for star $n$ at wavelength pixel
$j$, $\vecv(\ell_n)$ is the vectorizing function that takes as input the $K$ labels
$\ell_n$ for star $n$ and outputs functions of those labels as a vector of length
$D>K$, $\vectheta_j$ is a vector of length $D$ of parameters influencing the model at
wavelength pixel $j$, and $e_{jn}$ is the residual (noise).  Here we will only consider
vectorizing functions with polynomial expansions (e.g., $\teff^2$, see Section 
\ref{sec:a-simple-model}).  The noise values $e_{jn}$ can be considered to be drawn 
from a Gaussian distribution with zero mean and variance $\sigma_{jn}^2 + s_j^2$, where
$\sigma_{jn}^2$ is the variance in flux $y_{jn}$ and $s_j^2$ describes the excess 
variance at the $j$-th wavelength pixel.

At the \emph{training} step we fix the $K$-lists of labels for all the training set stars $n$.
At each wavelength pixel $j$, we then calculate the parameters $\vectheta_j$ and $s_j^2$
by optimizing the penalized likelihood function:
\begin{eqnarray}\label{eq:train}
\vectheta_j,s^2_j &\leftarrow& \argmin{\vectheta,s}\left[
    \sum_{n=0}^{N-1} \frac{[y_{jn}-\vecv(\ell_n)\cdot\vectheta]^2}{\sigma^2_{jn}+s^2}
    + \sum_{n=0}^{N-1} \ln(\sigma^2_{jn}+s^2) + \Lambda{}Q(\vectheta)
    \right]
  \quad ,
\end{eqnarray}

@@

Note that the $d$ subscript here is zero-indexed; the function $Q(\vectheta)$ does not act
on the (first) $\theta_0$ coefficient, as this is a `pivot point' or offset that we do not
expect to diminish with increasing regularization (e.g., see equation 
\ref{eq:vectorizer-three-label}).  In practice equation \ref{eq:train} is 
optimized by fixing $s_j^2 = 0$ to make equation~\ref{eq:train} a convex optimization 
problem, then we optimize for $\vectheta_j$, before solving for $s_j^2$.

@@

We sought to construct a training set of stars across the main-sequence, the
sub-giant branch, and the red giant branch.  We demanded stars with precisely measured
effective temperature $\teff$, surface gravity $\logg$, and elemental abundances
of O, Mg, Si, Ca, Al, Fe, and Ni.  This proved to be difficult because the magnitude
range of \rave\ does not overlap substantially with high-resolution spectroscopic
surveys.  The fourth internal data release of the \ges\ survey includes 
giant and main-sequence stars, but only 142 overlap with \rave, which is too small to
be a useful training set for our purposes.  The thirteenth data release from the Sloan
Digital Sky Survey \citep{sloan_dr13} includes labels for \apogee\ stars on the
giant branch and (uncalibrated values for) the main-sequence, but our tests indicated
that the \apogee\ main-sequence labels suffered from significant systematic effects.  
A flat, then `up-turning' main-sequence is present, and the metallicity gradient trends in 
the opposite direction with respect to $\logg$ on the main-sequence (i.e., metal-poor
stars incorrectly sit above an isochrone in a classical Hertzsprung-Russell diagram).
If we consider lower-resolution studies as potential training sets, there are 2,369
stars that overlap with \lamost\ --- of which 2,213 have positive S/N ratios in the 
$g$-band (\texttt{snrg}).  However, the labels are expectedly less precise given the
lower resolution, no detailed abundance information is available for main-sequence 
stars\footnote{Abundance information is available for \lamost\ stars from \citet{Ho_2016},
but that sample contains only giant stars}, and the \lamost\ lower main-sequence suffers
from the same systematic effects seen in \apogee\ data.  The \galah\ survey has a good 
overlap with \rave, but results from that sample are not yet precise enough for our 
purposes.

These constraints forced us to construct a heterogeneous training set.  Given previous
successes in transferring high S/N ratio labels from \apogee\ \citep{Ness_2015,
Ness_2016,Ho_2016,Casey_2016b}, we chose to use the 1,355 stars in the \apogee---\rave\ 
overlap sample for giant star labels in the training set.  Of these, about 900 are 
giants according to \apogee.  From this sample we selected stars to have: metallicity
determinations ([Fe/H] $> -5$); S/N ratios of $>20)$ in \apogee\ $>25$ in \rave; and 
we further required that the \aspcap\ pipeline did not report any peculiar flags 
(\texttt{ASPCAPFLAG = 0}).  These restrictions left us with 357 stars along the giant 
branch, with metallicities ranging from $[{\rm Fe/H}] = -1.62$ to 0.32.  Intermediate 
tests with globular cluster members showed that the metallicity range of the training 
set needed to extend below $[{\rm Fe/H}] \lesssim -2$ in order for our catalog to be 
practically useful.  Therefore, as we will describe in more detail below, we 
supplemented this sample with giant stars from the \epic\ catalog \citep{Huber_2016}.

Assembling a suitable training set for the main-sequence and sub-giant branch was less
trivial.  There are no spectroscopic studies that have a large enough sample size that
overlap with \rave\ and expand our required range in stellar parameters (e.g., FGKM-type 
stars).  Moreover, most of the spectroscopic studies we considered also showed a flat 
lower main-sequence, a systematic consequence of the analysis method adopted 
\citep[e.g., see][for a discussion]{Bensby_2014}.  For these reasons we chose to make 
use of the \epic\ catalog \citep{Huber_2016} for the training set labels on the 
main-sequence and sub-giant branch.  The \epic\ catalog follows from the successful
\project{Kepler} input catalog \citep{Brown_2011}, and provides probabilistic stellar 
classifications for 138,600 stars in the \project{K2} fields based on the 
astrometric, asteroseismic, photometric, and spectroscopic information available for
every star.  There are 4,611 stars that overlap between \epic\ and \rave.

\epic\ differs from the \project{Kepler} input catalog because \epic\ does not 
benefit from having narrow-band $DDO_{51}$ photometry in order to aid dwarf/giant 
classification.  Despite this limitation the labels in the \epic\ catalog have 
already been shown to be accurate and trustworthy \citep{Huber_2016}.  However, 
when the posteriors are wide (i.e., the quoted confidence intervals are large) 
due to limited information available, it is possible that a star has been 
misclassified.  This is most prevalent for sub-giants, where \citet{Huber_2016} 
note that $\approx55-70$\% of sub-giants are misclassified as dwarfs.  The 
probability of misclassification is usually quantified in the uncertainties given
for each star; most dwarfs that have a higher likelihood of being sub-giants have
large confidence intervals.  Therefore, requiring low uncertainties will decrease 
the total sample size, but in practice it removes most misclassifications.  The 
situation is far more favourable for dwarfs and giants.  Only $1-4$\% of giant 
stars are misclassified as dwarfs, and about 7\% of dwarfs are misclassified as 
giants.  To summarise, the \epic\ labels with narrow confidence intervals are 
usually of high fidelity, and any spurious misclassifications could be identified
if spectra were available.

We sought to have a small overlap between our giant and main-sequence star training
sets.  Most of our giant training set is encapsulated within $0 < \logg < 3.5$, 
however there is a sparse sampling of stars reaching to $\logg \approx 4$.  For
the \epic\ main-sequence/sub-giant star training set we required $\logg > 3.5$,
allowing for $\approx0.5$~dex of overlap between the two training sets.  We further
employed the following quality constraints: the upper and lower confidence intervals 
in $\teff$ must be below 150~K; the upper and lower confidence intervals in $\logg$ 
must be less than 0.15~dex; the $S/N$ of the \rave\ spectra must exceed 
30~pixel$^{-1}$; and $\teff \leqslant 6750$~K.  Unfortunately these strict constraints
removed most metal-poor stars, which we later found to cause the test labels to have
under-predicted abundances for dwarfs of low metallicity.  For this reason we relaxed
(ignored) those quality constraints for stars with $[{\rm Fe/H}] < -1$.  After training
a model based on main-sequence and giant stars (Section \ref{sec:the-model}), we found 
we could identify misclassifications by leave-one-out cross-validation.  However, we 
chose not to do this because the number of likely misclassifications in the training
set was negligible ($\approx1$\%), and the improvement in main-sequence test set labels
was minimal.  The distilled sample of the \rave--\epic\ overlap catalog contains 583 
stars (of 4,611).

We have constructed a justified training set for stars across the main-sequence, sub-giant,
and red giant branch.  However the lack of overlap between \rave\ and other works have
resulted in a somewhat peculiar situation.  Detailed abundances are available from \apogee\
for all giant stars in our sample, but only imprecise metallicities are available from
\epic\ for stars on the main-sequence and the sub-giant branch.  In the following section 
we will construct separate models for the giant branch and main-sequence.  We will
demonstrate the abundance labels are on the same scale, before combining the results from
multiple models to produce a single catalog.

@@

The model we introduced in Section~\ref{sec:the-model} is generic in the sense that there 
is no description for how complex the vectorizing function $\vecv(\ell)$ should be, or how
many $K$ labels are used.  Given previous successes using a second-order (quadratic) 
polynomial model \citep{Ness_2015,Ness_2016,Ho_2016,Casey_2016b}, we will first adopt a 
three-label ($\teff$, $\logg$, [Fe/H]) model for all (main-sequence and giant) stars. Thus, 
for our first set of model experiments,
\begin{eqnarray}\label{eq:vectorizer-three-label}
\vecv(\ell_n) \rightarrow \left[1, T_{{\rm eff},n}, \logg_n, [{\rm Fe/H}]_n, T_{{\rm eff},n}^2, \logg_n\cdot{}T_{{\rm eff},n}, \feh_n\cdot{}T_{{\rm eff},n}, \logg_n^2, \feh_n\cdot\logg_n, \feh_n^2\right]
\end{eqnarray}
